---
title: "🌍 Globetrotters"
output:
  html_document:
    self_contained: false
runtime: shiny
output_file: "Interactive_Map.html" 
---

<!-- Google Font + Styles -->
<link href="https://fonts.googleapis.com/css2?family=Patrick+Hand&display=swap" rel="stylesheet">

<style>
body {
  background: linear-gradient(
    rgba(245, 222, 179, 0.25),
    rgba(245, 222, 179, 0.25)
  ),
  url("https://www.transparenttextures.com/patterns/paper-fibers.png");
  font-family: 'Patrick Hand', sans-serif;
}

.logo-title {
  text-align: center;
  font-size: 64px;
  color: #1d3557;
  margin-bottom: 10px;
}

.main-card {
  max-width: 1200px;
  margin: 40px auto;
  padding: 35px;
  background-color: rgba(255, 255, 255, 0.92);
  border-radius: 18px;
  box-shadow: 0 6px 25px rgba(0,0,0,0.08);
}

.round-title {
  text-align: center;
  color: #1d3557;
  border: 2px dashed rgba(29, 53, 87, 0.2);
  display: inline-block;
  padding: 8px 20px;
  border-radius: 12px;
}

.input-row {
  display: flex;
  justify-content: center;
  align-items: center;
  gap: 15px;
  margin-bottom: 20px;
}

#username {
  padding: 10px 15px;
  border-radius: 10px;
  border: 1px solid #ccc;
  font-size: 18px;
  font-family: 'Patrick Hand', cursive;
}

.btn-primary-custom {
  padding: 10px 20px;
  border-radius: 10px;
  border: none;
  background-color: #457b9d;
  color: white;
  font-size: 18px;
  cursor: pointer;
  transition: all 0.2s ease;
}

.btn-primary-custom:hover {
  background-color: #1d3557;
  transform: scale(1.05);
}
</style>

<div class="logo-title">Round 8</div>
<div class="main-card">
<h2 class="round-title">Guess the Location</h2>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "asis"
)

library(shiny)
library(leaflet)
library(geosphere)
library(googlesheets4)

# Authenticate with Google Sheets (run interactively first)
gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets")

# Your Google Sheet ID
sheet_id <- "1ApiK4wU_XZ4AIRfblEHg6Lnm-shaso9US8mYTj3Hpu0"
```


```{r}
# Shiny UI
fluidPage(
  div(class = "input-row",
      textInput("username", NULL, placeholder = "Enter username", width = "250px"),
      actionButton("submit_guess", "🎯 Confirm Guess", class = "btn-primary-custom")
  ),
  leafletOutput("map", height = "500px"),
  br(),
  verbatimTextOutput("info")
)
# Shiny Server
current_guess <- reactiveVal(NULL)

# Render map
output$map <- renderLeaflet({
  leaflet() %>%
    addTiles() %>%
    setView(lng = 0, lat = 20, zoom = 2)
})

# Click → place marker only
observeEvent(input$map_click, {
  lat <- input$map_click$lat
  lng <- input$map_click$lng
  current_guess(c(lat = lat, lng = lng))
  
  leafletProxy("map") %>%
    clearMarkers() %>%
    addMarkers(lng = lng, lat = lat)
  
  output$info <- renderPrint({
    paste("📍 Selected location:", round(lat, 4), round(lng, 4))
  })
})

# Submit → validate + save to Google Sheet
observeEvent(input$submit_guess, {
  guess <- current_guess()
  username <- input$username
  
  if (is.null(guess)) {
    output$info <- renderPrint({"❌ Click on the map first!"})
    return()
  }
  
  if (is.null(username) || username == "") {
    output$info <- renderPrint({"❌ Please enter a username!"})
    return()
  }
  
  lat <- guess["lat"]
  lng <- guess["lng"]
  
  new_row <- data.frame(
    username = username,
    lat = lat,
    lng = lng,
    time = Sys.time()
  )
  
  # Append to Google Sheet
  sheet_append(ss = sheet_id, data = new_row)
  
  # Example distance calculation
  true_lat <- 50
  true_lng <- 10
  dist <- distHaversine(c(lng, lat), c(true_lng, true_lat))
  
  output$info <- renderPrint({
    paste(
      "✅ Guess submitted!",
      "\n👤 Player:", username,
      "\n📍 Your guess:", round(lat, 4), round(lng, 4),
      "\n📏 Distance (meters):", round(dist)
    )
  })
})
