---
output:
  html_document:
   self_contained: false
---

<style>
body {
  background: linear-gradient(
    rgba(245, 222, 179, 0.25),
    rgba(245, 222, 179, 0.25)
  ),
  url("https://www.transparenttextures.com/patterns/paper-fibers.png"); /* subtle paper texture */
  
  font-family: 'Patrick Hand', sans-serif;
}

button, select {
  font-family: 'Patrick Hand', cursive;
}

/* ⭐ Main content card */
.main-card {
  max-width: 1200px;
  margin: 40px auto;
  padding: 35px;

  background-color: rgba(255, 255, 255, 0.92);
  border-radius: 18px;

  box-shadow: 0 6px 25px rgba(0,0,0,0.08);

  border: 1px solid rgba(0,0,0,0.05);
}

/* ⭐ Subtle “passport stamp” style for round titles */
.round-title {
  font-family: 'Patrick Hand', cursive;
  text-align: center;
  color: #1d3557;

  border: 2px dashed rgba(29, 53, 87, 0.2);
  display: inline-block;
  padding: 8px 20px;
  border-radius: 12px;

  background-color: rgba(255,255,255,0.6);
}

/* ⭐ Tourguide text styling */
.tourguide-box {
font-family: 'Patrick Hand', cursive;
  text-align: center;
  font-size: 22px;
  margin-top: 25px;

  background-color: rgba(255,255,255,0.7);
  padding: 15px;
  border-radius: 12px;

  border: 1px dashed rgba(69, 123, 157, 0.3);
}
</style>

<style>
body {
background-color: rgba(236, 214, 178, 0.3); /* ⭐ soft sand color */
}
</style>

<style>
/* DT tables font */
table.dataTable {
font-size: 22px;
  font-family: 'Patrick Hand', cursive !important;
}
.dataTables_wrapper {
  font-family: 'Patrick Hand', cursive !important;
}
</style>

<style>
/* ⭐ DT global table header styling */
#global_page table.dataTable thead th {
  background-color: #457b9d !important;
  color: white !important;
  font-weight: bold !important;
  text-align: center;
  font-family: 'Patrick Hand', cursive !important;
}
#global_page table.dataTable tbody td {
  text-align: center;
  font-family: 'Patrick Hand', cursive !important;
}
#global_page table.dataTable tbody td:nth-child(2) {
  text-align: left; /* Player column */
}
</style>

<div style="text-align: center; margin-bottom: 30px;">

  <h1 style="
    font-family: 'Patrick Hand', cursive;
    font-size: 64px;
    color: #1d3557;
    margin-bottom: 10px;
  ">
    🌍 Globetrotters
  </h1>

</div>

<div class="main-card">


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "asis"
)
```

```{r}

library(dplyr)
library(gt)
library(scales)
library(DT)

manual_rounds <- data.frame(
  round = c(1,1,1,1,1,
            2,2,2,2,2,
            3,3,3,3,3,
            4,4,4,4,4,
            5,5,5,5,5,5,5,
            6,6,6,6,6,6,6,6),
  player = c("Julius","Kathy","Uli","Ria","Leon",
             "Julius","Kathy","Uli","Ria","Leon",
             "Julius", "Kathy", "Uli", "Leon", "Kamil",
             "Kathy", "Uli", "Ria", "Leon", "Henri",
             "Julius", "Kathy", "Ria", "Henri","Freddy", "Leonhard", "Qi",
             "Julius", "Kathy", "Uli", "Ria", "Leon", "Henri", "Leonhard", "Qi"),
  Distance = c(0, 166, 912, 912, 3660,
               0, 170000, 136000, 169000,8,
               0, 6, 3470, 57400, 9720,
               0, 26900, 26900, 48500, 3080,
               69400, 52200, 0, 68100, 308000, 48100, 20,
               132000, 227000, 129000, 191000, 76800, 0, 155000, 32900),
  role = c("Tourguide","Traveler","Traveler","Traveler","Traveler",
           "Tourguide","Traveler","Traveler","Traveler","Traveler",
           "Tourguide","Traveler","Traveler","Traveler","Traveler",
           "Tourguide", "Traveler","Traveler","Traveler","Traveler",
           "Traveler", "Traveler","Tourguide","Traveler","Traveler","Traveler","Traveler",
           "Traveler", "Traveler","Traveler","Traveler","Traveler","Tourguide","Traveler", "Traveler"),
  Bonusview = c("no","yes","no","no","no",
                "no", "no", "no", "no", "yes",
                "no", "no", "no", "no", "no",
                "no", "no", "no", "no", "no",
                "no", "yes", "no", "no", "no", "no", "yes",
                "no", "no", "no", "no", "no", "no", "no", "no"
                ),
  date = as.Date(c("2026-03-29","2026-03-29","2026-03-29","2026-03-29","2026-03-29",
                   "2026-03-31","2026-03-31","2026-03-31","2026-03-31","2026-03-31",
                   "2026-04-01","2026-04-01","2026-04-01","2026-04-01","2026-04-01",
                   "2026-04-03","2026-04-03","2026-04-03","2026-04-03","2026-04-03",
                   "2026-04-05","2026-04-05","2026-04-05","2026-04-05","2026-04-05","2026-04-05","2026-04-05",
                   "2026-04-06","2026-04-06","2026-04-06","2026-04-06","2026-04-06","2026-04-06","2026-04-06", "2026-04-06"))  # ⭐ NEW
)
```


```{r}
# ⭐ NEW: Dynamic dropdown with dates for each round

all_rounds <- sort(unique(manual_rounds$round))
# ⭐ NEW: create a date for each round
for(r in all_rounds){
  
  round_date <- manual_rounds %>%
    filter(round == r) %>%
    pull(date) %>%
    unique()

  cat(paste0(
    "<option value='round_", r, "'>🎯 Round ", r, " (",
    format(round_date, "%b %d, %Y"),
    ")</option>"
  ))
}

cat("<div style='text-align:center; margin-bottom:20px;'>")

# Global Rankings button
cat("<button onclick=\"showGlobal()\" style='padding:10px 20px; font-size:18px; margin-bottom:10px;'>🌍 Global Rankings</button><br>")

# Dropdown for rounds
cat("<select id='roundSelect' onchange=\"showPage(this.value)\" style='padding:10px 20px; font-size:18px;'>")
cat("<option value='' disabled selected>Select Round</option>")   # ⭐ placeholder

# ⭐ Loop to create dropdown options with dates
for(r in all_rounds){

  round_date <- manual_rounds %>%
    filter(round == r) %>%
    pull(date) %>%
    unique()

  cat(paste0(
    "<option value='round_", r, "'>🎯 Round ", r, " (", 
    format(round_date, "%b %d, %Y"), 
    ")</option>"
  ))

}
cat("</select>")

cat("</div>")

# ⭐ GLOBAL PAGE (visible by default)
cat("<div id='global_page' style='display:block;'>")

cat("<div style='width:100%;'>")

# Step 1: Calculate Travel Miles for each player in each round
round_miles <- manual_rounds %>%
  group_by(round) %>%
  
  # ⭐ STEP 1: Travelers with Bonusview penalty
  mutate(`Travel Miles` = ifelse(
    role == "Traveler",
    5000 - (Distance / 200) - ifelse(Bonusview == "yes", 1000, 0),
    NA
  )) %>%
  
  # ⭐ STEP 2: Count Bonusview "yes"
  mutate(bonus_count = sum(Bonusview == "yes" & role == "Traveler")) %>%
  
  # ⭐ STEP 3: Tourguide calculation + bonus
  mutate(`Travel Miles` = ifelse(
    role == "Tourguide",
    (max(`Travel Miles`, na.rm = TRUE) - min(`Travel Miles`, na.rm = TRUE)) +
    (bonus_count * 200),
    `Travel Miles`
  )) %>%
  
  ungroup() %>%
  select(-bonus_count)

# Step 2: Aggregate across all rounds for global table
global_table <- round_miles %>%
  group_by(player) %>%
  summarise(
    Travelers = sum(role == "Traveler"),
    Tourguides = sum(role == "Tourguide"),
    `Travel Miles` = sum(`Travel Miles`),
    .groups="drop"
  ) %>%
  mutate(
    `Passport Value` = `Travel Miles` / (Travelers + (Tourguides / 2))
  ) %>%
  arrange(desc(`Passport Value`)) %>%
  mutate(Rank = row_number()) %>%
  select(Rank, Player = player, Travelers, Tourguides, `Travel Miles`, `Passport Value`)

# ⭐ Convert top 3 ranks into medals
global_table$Rank <- as.character(global_table$Rank)
global_table$Rank[global_table$Rank == "1"] <- "🥇"
global_table$Rank[global_table$Rank == "2"] <- "🥈"
global_table$Rank[global_table$Rank == "3"] <- "🥉"

# ⭐ NEW: Make gt table INTERACTIVE (click-to-sort)
datatable(
  global_table,
  options = list(
    pageLength = 10,
    autoWidth = TRUE,
    dom = 't',          # optional: hides extra DT controls to match round page style
    ordering = TRUE
  ),
  rownames = FALSE,
  class = "stripe hover",
  colnames = c(
    "Rank",
    "Player",
    "Travelers",
    "Tourguides",
    "Travel Miles",
    "Passport Value"
  )
) %>%
  formatRound("Travel Miles", 2) %>%
  formatRound("Passport Value", 2) %>%
  formatStyle(
    columns = names(global_table),
    'text-align'='center'
  ) %>%
  formatStyle(
    columns = "Player",
    'text-align'='left'
  )%>% formatStyle(
    'Rank',
    target = 'row',
    backgroundColor = DT::styleEqual(
      c("🥇","🥈","🥉"),
      c("#fff7d6","#f0f0f0","#fdebd0")  # subtle pastel highlights instead of gold/silver/bronze
    ),
    fontWeight = DT::styleEqual(
      c("🥇","🥈","🥉"),
      c("bold","bold","bold")
    )
)
cat("</div>")
cat("</div>")
```


```{r}
# Get all rounds
all_rounds <- sort(unique(manual_rounds$round))

# ⭐ NEW: Vector of links per round – you can fill your own URLs here
# Example: round_links <- c("link_for_round_1", "link_for_round_2", ...)
round_links <- c(
  "https://juliusmarz.github.io/Globetrotter/Round1.html",
  "https://juliusmarz.github.io/Globetrotter/Round2.html",
  "https://juliusmarz.github.io/Globetrotter/Round3.html",
  "https://juliusmarz.github.io/Globetrotter/Round4.html",
  "https://juliusmarz.github.io/Globetrotter/Round5.html",
  "https://juliusmarz.github.io/Globetrotter/Round6.html"
)
names(round_links) <- all_rounds

# ⭐ NEW: Bonusview images per round
round_images <- c(
  "Round1_bonus.jpeg",
  "Round2_bonus.jpeg",
  "Round3_bonus.jpeg",
  "Round4_bonus.jpeg",
  "Round5_bonus.jpeg",
  "Round6_bonus.jpeg"
)
names(round_images) <- all_rounds

# Loop through each round
for(r in all_rounds){

  # ⭐ Start div for this round (hidden by default)
  cat(paste0("<div id='round_", r, "' style='display:none;'>"))

  # ⭐ Dynamic title for each round
cat("<div style='text-align:center; margin-bottom:15px;'>")
cat(paste0("<div class='round-title'>🌍 Round ", r, "</div>"))
cat("</div>")
cat("<div style='width:100%; max-width:1200px; margin:0 auto;'>")

  # Table generation filtered by current round
# Assign a random "Distance" to each player for this example
round_table <- manual_rounds %>%
  filter(round == r)

# Calculate Travel Miles according to rules
# Travelers base calculation + Bonusview penalty
round_table <- round_table %>%
  mutate(`Travel Miles` = ifelse(
    role == "Traveler",
    5000 - (Distance / 200) - ifelse(Bonusview == "yes", 1000, 0),
    NA
  ))
# Step 3: Calculate Travel Miles for Tourguide
traveler_miles <- round_table$`Travel Miles`[round_table$role == "Traveler"]

# Count Bonusview "yes"
bonus_count <- sum(round_table$Bonusview == "yes" & round_table$role == "Traveler")

round_table <- round_table %>%
  mutate(`Travel Miles` = ifelse(
    role == "Tourguide",
    (max(traveler_miles) - min(traveler_miles)) + (bonus_count * 200),
    `Travel Miles`
  ))
# Rank players by Travel Miles descending
round_table <- round_table %>%
  arrange(desc(`Travel Miles`)) %>%
  mutate(Rank = row_number()) %>%
  select(Rank, Player=player, `Distance (m)` = Distance, Bonusview, `Travel Miles`)

  round_table %>%
    gt() %>%
    opt_table_font(
  font = list(gt::google_font("Patrick Hand"))
)%>%
    cols_align(align="center", -Player) %>%
    cols_align(align="left", Player) %>%
    opt_row_striping() %>%
    tab_style(
      style=list(cell_fill(color="#457b9d"),
                 cell_text(color="white", weight="bold")),
      locations=cells_column_labels(everything())
    ) %>%
    tab_style(
      style=list(cell_text(weight="bold")),
      locations=cells_body(rows=Rank<=3)
    ) %>%
    text_transform(
      locations=cells_body(columns=Rank),
      fn=function(x){
        ifelse(x==1,"🥇",ifelse(x==2,"🥈",ifelse(x==3,"🥉",x)))
      }
    ) %>%
    tab_options(
      table.font.size=px(22),
      data_row.padding=px(16),
      container.width=pct(100),
      column_labels.padding=px(14)
    ) %>%
    print()

  cat("</div>")  # End flex container

  # ⭐ NEW: Text about the tourguide + location link
 tourguide_name <- manual_rounds %>%
  filter(round == r, role == "Tourguide") %>%
  pull(player)
 
cat(paste0(
  "<div class='tourguide-box'>",
  
  "<div style='margin-bottom:10px;'>",
  "🧭 The tourguide in this round was: <strong>", tourguide_name, "</strong>",
  "</div>",

  # ⭐ BUTTON ROW
  "<div style='display:flex; justify-content:center; gap:15px;'>",

    # 📍 LOCATION BUTTON
    "<a href='", round_links[r], "' target='_blank' ",
    "style='text-decoration:none; padding:10px 15px; border-radius:10px; ",
    "background-color:#457b9d; color:white; font-size:16px;'>",
    "📍 View location</a>",

    # 📸 BONUSVIEW BUTTON
    "<button onclick=\"toggleImage('img_", r, "')\" ",
    "style='padding:10px 15px; border-radius:10px; border:none; ",
    "background-color:#e63946; color:white; font-size:16px; cursor:pointer;'>",
    "📸 Bonusview</button>",

  "</div>",

  # ⭐ IMAGE (HIDDEN BY DEFAULT)
  "<div id='img_", r, "' style='display:none; margin-top:15px;'>",
    "<img src='", round_images[r], "' ",
    "style='max-width:100%; border-radius:12px; box-shadow:0 4px 15px rgba(0,0,0,0.15);'>",
  "</div>",

  "</div>"
))
  cat("</div>")  # End round div
}
```

<!-- ⭐ NEW: Page switching script -->

<script>
function showPage(pageId) {
  // Hide global
  document.getElementById('global_page').style.display = 'none';
  
  // Hide all rounds
  var rounds = document.querySelectorAll("[id^='round_']");
  rounds.forEach(function(r){ r.style.display = 'none'; });

  // Show selected
  var el = document.getElementById(pageId);
  if(el) el.style.display = 'block';
}

function showGlobal() {
  // Hide all rounds
  var rounds = document.querySelectorAll("[id^='round_']");
  rounds.forEach(function(r){ r.style.display = 'none'; });

  // Show global
  document.getElementById('global_page').style.display = 'block';

  // ⭐ RESET DROPDOWN 
  var dropdown = document.getElementById('roundSelect');
  if(dropdown) dropdown.selectedIndex = 0;
}

function toggleImage(id) {
  var el = document.getElementById(id);
  if (el.style.display === "none") {
    el.style.display = "block";
  } else {
    el.style.display = "none";
  }
}
</script>
</div>